B\'{e}zier $\bar{B}$ projection

### 2018-01-26 projection1120.tex
Revisions.

We have demonstrated the performance of the approach in the context of shear deformable beams (to alleviate transverse shear locking) and nearly incompressible elasticity problems (to alleviate volumetric locking). The proposed method reduces locking errors and achieves (nearly) optimal convergence rates \added{ for the symmetric method and optimal rates for the non-symmetric method}. The cases where optimal rates were not achieved \added{when using the the symmetric formulation are a symptom of the fact that the symmetric formulation is not consistent with the mixed formulation}.

>>>>

We have demonstrated the performance of the approach in the context of shear deformable beams (to alleviate transverse shear locking) and nearly incompressible elasticity problems (to alleviate volumetric locking). The proposed method reduces locking errors and achieves (nearly) optimal convergence rates \added{ for the symmetric method and optimal rates for the non-symmetric method}. The cases where optimal rates were not achieved \added{when using the the symmetric formulation are a symptom of the fact that the symmetric formulation is not directly related to a variational principle so it may not satisfy the inf-sup condition}.
